### 2018-09-17 ms.tex
Fix table3.

\begin{table}[!ht]
\begin{adjustwidth}{-2.25in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
\centering
\caption{
{\bf Summary of coverage of 80\% credible intervals for.}}
\begin{tabular}{llllll}
\hline
{\bf Holdout data} & {\bf crossvalidation} & {\bf Country} &  {\bf Points} & {\bf Polygons} & {\bf Joint} \\
\thickhline 
Incidence & Random & Indonesia &  0.11 &  0.77 &   0.79\\
&& Senegal &  0.11 &  0.80 &   0.85\\
&& Madagascar &  0.59 &  0.82 &   0.77\vspace{1mm}\\
& Spatial & Indonesia &  0.11 &  0.77 &   0.79\\
&& Senegal &  0.11 &  0.80 &   0.85\\
&& Madagascar &  0.59 &  0.82 &   0.77\vspace{3mm} \\
Prevalence & Random & Indonesia &  0.83 &  0.66 &   0.85\\
&& Senegal &  0.90 &  0.88 &   0.79\\
&& Madagascar &  0.93 &  0.68 &   0.83\vspace{1mm}\\
& Spatial & Indonesia & -0.35 & -0.05 &  -0.01\\
&& Senegal &  0.90 &  0.88 &   0.79\\
&& Madagascar &  0.93 &  0.68 &   0.83\\
\end{tabular}
\begin{flushleft}

>>>>

\begin{table}[!ht]
\begin{adjustwidth}{-2.25in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
\centering
\caption{
{\bf Summary of coverage of 80\% credible intervals for.}}
\begin{tabular}{llllll}
\hline
{\bf Holdout data} & {\bf crossvalidation} & {\bf Country} &  {\bf Points} & {\bf Polygons} & {\bf Joint} \\
\thickhline 
Incidence & Random & Indonesia & 0.10 & 0.76 &  0.77\\
&& Senegal & 0.69 & 0.82 &  0.78\\
&& Madagascar & 0.73 & 0.82 &  0.78\vspace{1mm}\\
& Spatial & Indonesia & 0.10 & 0.76 &  0.77\\
&& Senegal & 0.69 & 0.82 &  0.78\\
&& Madagascar & 0.73 & 0.82 &  0.78\vspace{3mm} \\
Prevalence & Random & Indonesia & 0.83 & 0.59 &  0.77\\
&& Senegal & 0.87 & 0.69 &  0.80\\
&& Madagascar & 0.83 & 0.69 &  0.80\vspace{1mm}\\
& Spatial & Indonesia & 0.54 & 0.36 &  0.38\\
&& Senegal & 0.87 & 0.69 &  0.80\\
&& Madagascar & 0.83 & 0.69 &  0.80\\
\end{tabular}
\begin{flushleft}
